A Comparison of Graph Processing Systems

### 2020-09-12 documentation/paper/sections/preliminiaries.tex
paper prelimiaries push and pull

In general such an operator can change the structure of the \emph{neighbourhood} too.
But in the following we assume, that an operator changes only \emph{labels} of vertices or edges in the \emph{neighbourhood}.
Often this operator can be implemented in two different ways, called \emph{push style} or \emph{pull style}.
A \emph{push-style} operator reads the value of the \emph{active} vertex or edge and updates the values of its \emph{neighborhood}.
In contrast the \emph{pull-style} operator reads all values of its \emph{neighborhood} and updates the value of the \emph{active} vertex or edge.

>>>>

In general such an operator can change the whole structure of the \emph{neighbourhood}.
But in the following we assume, that an operator changes only \emph{labels} of vertices or edges in the \emph{neighbourhood}.
\emph{Labels} of edges also called \emph{weights}.
Often this operator can be implemented in two different ways, called \emph{push style} or \emph{pull style}.
A \emph{push-style} operator reads the \emph{label} of the \emph{active} vertex or edge and updates the \emph{label} of its \emph{neighborhood}.
In contrast the \emph{pull-style} operator reads all values of its \emph{neighborhood} and updates the value of the \emph{active} vertex or edge.
